Multipoint Approximation Method for Large Scale Design Optimization Problems Under Uncertainty

### 2018-01-12 2018/LION_Toropov/LION2018.tex
Minor corrections

Optimization under uncertainty deals with responses $F(\pmb x,\pmb y)$ that depend on deterministic design variables $\pmb x$ and random ‘environmental’ variables $\pmb y$. Uncertainty in the design variables can also be modelled by introducing additional random variables, e.g. as additive or multiplicative noise. In this case, the responses $F(\pmb x,\pmb y)$ receive as input the sum $\pmb x+\pmb u$ (if the noise is additive), where $\pmb u$ is a random variable with a known probability distribution, yielding responses depending on $\pmb x,\; \pmb u$ and $\pmb y$. Randomness in $\pmb u$ and $\pmb y$ induces randomness in the responses $F(\pmb x+\pmb u,\pmb y)$. To convert them into deterministic functions, that can be optimized, a mapping $R$, called the \textit{risk measure} \cite{RockafellarUryasev2000} or \textit{robustness measure} \cite{SchillingsSchulz2015}, is applied to the responses. The result is then a deterministic function of the design variables: $\widetilde{F}(\pmb x)=R(F(\pmb x+\pmb u, \pmb y))$. The choice of a particular risk measure $R$ reflects the designer's attitude towards the risk of sub-optimal performance or constraint violation. For example, $R$ can be a combination of the mean and standard deviation of $F(\pmb x+ \pmb u,\pmb y)$ with respect to the joint probability distribution of $\pmb u$ and $\pmb y$ or a quantile of the distribution of $F(\pmb x+ \pmb u,\pmb y)$, i.e. such a value that the random variable of $F(\pmb x+\pmb u,\pmb y)$ exceeds it with a given, typically small, probability.

Computations of the risk measures typically involve evaluation of high-dimensional integrals, which becomes a challenging task if the number of design variables and/or environmental variables is large. The problem becomes even more difficult if the original responses are computationally expensive, which is the case, for example, in computational fluid dynamics (CFD), where one function evaluation may take hours of even days. Therefore, direct computation of the risk measures using original responses becomes infeasible and therefore approximations of responses, also referred to as metamodels, need to be used.

@@

It is useful to start with a brief description of the deterministic version of MAM. A typical formulation of a constrained optimization problem that MAM works with is as follows:
\begin{equation}
  \label{eq:problem}
  \begin{array}{c}
  \min\limits_{a_i \le x_i \le b_i}F_0(\pmb x) \\
  s.t.\; F_j(\pmb x) \le 1,\; j=1,\dots ,M,
  \end{array}
\end{equation}
where $\pmb x$ is the vector of design variables, $\pmb a$ and $\pmb b$ are the lower and upper bounds for the design variables, respectively, $F_0(\pmb x)$ is the objective function, and $F_j(\pmb x)$ are the constraints. The numbers of design variables and constraints are $n$ and $M$, respectively. MAM attempts to solve this problem by using approximations of the objective function and constraints in a series of trust regions. The trust region strategy seeks to zoom in on the region where the constrained minimum is achieved. It aims at finding a trust region that is sufficiently small for the approximations to be of sufficiently good quality to improve the design, and that contains the point of the constrained minimum as its interior point. The main loop of the MAM is organized as follows.

Algorithm 1 (deterministic MAM).
\begin{enumerate}
\item Initialization: choose a starting point $\pmb x^0$ and initial trust region $[\pmb a^0, \pmb b^0]$ such that $\pmb x^0 \in [\pmb a^0, \pmb b^0]$.
\item At the $k$-th iteration the current approximation to the constrained minimum is $\pmb x^k$, the current trust region is $[\pmb a^k, \pmb b^k] \subset [\pmb a^0, \pmb b^0]$.
  \begin{enumerate}[label=(\alph*)]
    \item Design of Experiments (DoE): a set of points $\pmb x_k^i \in [\pmb a^k, \pmb b^k]$ is chosen to be used for approximation building. Responses are evaluated at the DoE points and approximations are built using the obtained values. Currently, the pool of approximation methods available in MAM consists of a metamodel assemblies \cite{PolynkinToropov2012} and the moving least-squares metamodels \cite{LancasterSalkauskas1981,Liszka1984,ChoiYounYang2001,ToropovSchrammSahaiJones2005}. Other metamodel types could be used as well.

    Denote the approximate objective function and constraints by $\widetilde{F}_0(\pmb x)$ and $\widetilde{F}_j(\pmb x)$, respectively.
    \item The original optimization problem (\ref{eq:problem}) is replaced by the following problem:
    \begin{equation}
      \label{eq:problem_approx}
      \begin{array}{c}
      \min\limits_{a_i^k \le x_i ^k\le b_i}\widetilde{F}_0(\pmb x) \\
      s.t.\; \widetilde{F}_j(\pmb x) \le 1,\; j=1,\dots ,M,
      \end{array}
    \end{equation}
    The approximate problem (\ref{eq:problem_approx}) is solved using Sequential Quadratic Programming (SQP) and the solution of this problem determines the center of the next trust region.
    \item The size of the next trust region is determined depending on the quality of approximations at the previous iteration, on the history of the points $\pmb x^k$, and on the size of the current trust region \cite{KeulenToropovMarkine1996}.
    \item The termination criterion is checked (it is a part of the trust region strategy and depends on the position of the point $\pmb x^{k+1}$ in the current trust region, the size of the current trust region and the quality of approximations). If the termination criterion is satisfied, the algorithm proceeds to step 3. Otherwise, it returns to step 2.
  \end{enumerate}
  \item Optimization terminates. The obtained approximation to the solution of the problem (\ref{eq:problem}) is $\pmb x^{k+1}$.
\end{enumerate}

@@

The presence of uncertainties in the responses requires certain reformulations in the problem statement (\ref{eq:problem}). Informally, the optimization problem with uncertainty can be written as follows:
\begin{equation}
  \label{eq:problem_unc}
  \begin{array}{c}
  \min\limits_{a_i \le x_i \le b_i}F_0(\pmb x + \pmb u, \pmb y) \\
  s.t.\; F_j(\pmb x + \pmb u, \pmb y) \le 1,\; j=1,\dots ,M,
  \end{array}
\end{equation}
where the random variable $\pmb u$ represents (additive) noise in the design variables and $\pmb y$ is the environmental variable, representing input to the responses that cannot be influenced by the designer. This problem statement is not precise since the random responses $F_0 (\pmb x+\pmb u,\pmb y),\; F_j (\pmb x+\pmb u,\pmb y)$ cannot be directly optimized. Therefore, a risk measure $R$ needs to be applied to the objective and the constraints:
\begin{equation}
  \label{eq:problem_unc_r}
  \begin{array}{c}
  \min\limits_{a_i \le x_i \le b_i}R_{\pmb u,\pmb y}(F_0)(\pmb x) \\
  s.t.\; R_{\pmb u,\pmb y}(F_j)(\pmb x) \le 1,\; j=1,\dots ,M,
  \end{array}
\end{equation}
where the subscript in $R_{\pmb u,\pmb y}$ indicates that the variables $\pmb u$ and $\pmb y$ ‘collapse’ when the risk measure is applied and the result only depends on $\pmb x$. The choices of risk measure will be discussed in Section \ref{sec:risk}. Here the changes in the Algorithm 1 that are necessary to solve the problem (\ref{eq:problem_unc_r}) are discussed.

First, it needs to be decided on whether to build metamodels for the risk measure $R_{\pmb u,\pmb y}(F_j)(\pmb x)$ or for the original responses $F_j (\pmb x+ \pmb u,\pmb y)$. The first option may seem attractive due to the simplicity of its implementation in Algorithm 1 but the deciding argument has to be that of the computational cost associated with the evaluation of either function. On the one hand, one evaluation of the function $R_{\pmb u,\pmb y}(F_j)(\pmb x)$ involves computing one or several integrals of the original response $F_j(\pmb x+ \pmb u,\pmb y)$ over the distribution of $\pmb u$ and $\pmb y$, which requires many evaluations of the original response. On the other hand, the dimensionality of the argument of $R_{\pmb u,\pmb y}(F_j)(\pmb x)$ is less than that of the argument of $F_j(\pmb x+ \pmb u,\pmb y)$, therefore, in principle, fewer function evaluations are needed to approximate the former than the latter. In practice, this may be a matter of a trade-off between the two abovementioned effects that depends on the proportion between the numbers of design variables $n$ and the environmental variables $n_e$ and on the complexity of the integration method and metamodeling method used. If the number if design variables is significantly larger than the number of environmental variables, which is often the case and which is assumed in this paper, building metamodels for the original responses $F_j(\pmb x+ \pmb u,\pmb y)$ is preferred.

@@

Algorithm 2 (MAM under uncertainty).
\begin{enumerate}
%  \item Initialization: choose a starting point $\pmb x_0 \in {\Bbb R}^n$. 
  \item Initialization: choose a starting point $\pmb x_0 \in {\pmb R}^n$. 
	Choose an initial trust region $[\pmb a^0,\pmb b^0]$ in the combined space of design variables and environmental variables. 
	Ensure that the initial guess $\pmb x_0$ belongs to the projection of the initial trust region onto the subspace of design variables. The projection of the initial trust region onto the subspace of environmental variables must cover the region where the realizations of the random variable y are likely to be. The coordinates of the trust region corresponding to the environmental variables will not be changed in the course of optimization. Typically, the trust region along the coordinates corresponding to the $i$-th environmental variable is centered at the mean of the $i$-th environmental variable and has the width of six of its standard deviations.
  \item At the $k$-th iteration the current approximation to the constrained minimum is $\pmb x^k$, the current trust region is $[\pmb a^k,\pmb b^k]$.
  \begin{enumerate}[label=(\alph*)]
    \item Design of Experiments (DoE): a set of points $(x_i^k,y_i^k)\in [\pmb a^k,\pmb b^k]$ is chosen that will be used to build approximations. Responses are evaluated at the DoE points and approximations are built using the obtained values.
    Denote the approximate objective function and constraints by $\widetilde{F}_0(\pmb x, \pmb y)$ and $\widetilde{F}_j(\pmb x, \pmb y)$, respectively.
    \item The original optimization problem is replaced by the following problem:
    \begin{equation}
      \label{eq:problem_u_tilde}
      \begin{array}{c}
      \min\limits_{a_i \le x_i \le b_i}R_{\pmb u,\pmb y}(\widetilde{F}_0)(\pmb x) \\
      s.t.\; R_{\pmb u,\pmb y}(\widetilde{F}_j)(\pmb x) \le 1,\; j=1,\dots ,M,
      \end{array}
    \end{equation}
    The risk measures are calculated using the metamodels obtained in the previous step. Integrals that arise during this process are calculated with respect to the joint distribution of $\pmb u$ and $\pmb y$. This distribution is assumed to be fixed.
    The approximate problem (\ref{eq:problem_u_tilde}) is solved using Sequential Quadratic Programming (SQP) and the center of the next trust region $\pmb x^{k+1}$ is determined as the solution of this problem. The optimization runs in a subspace of the space where metamodels are built: metamodels are defined in the combined space of design variables and environmental variables, whilst optimization runs in the subspace of the design variables.
    \item The trust region is updated. The size of the trust region along the dimensions corresponding to the environmental variables is unchanged. The size of the next trust region along the dimensions corresponding to the design variables is determined depending on the quality of approximations at the previous iteration, on the history of the points $\pmb x^k$, and on the size of the current trust region according to the trust region strategy explained in \cite{KeulenToropovMarkine1996}.
    \item The termination criterion is checked. If the termination criterion is satisfied, the algorithm proceeds to step 3. Otherwise, it returns to step 2
  \end{enumerate}
  \item Optimization terminates. The obtained approximation to the optimum is $\pmb x^{k+1}$.
\end{enumerate}

@@

As it has been already said, a risk measure is a mapping that transforms a random response $F(\pmb x+ \pmb u,\pmb y)$  into a deterministic function that can be optimized. Next we provide some examples of risk measures \cite{RockafellarUryasev2000,SchillingsSchulz2015}.

\begin{itemize}
  \item $R(F)=\mu(F)$ where $\mu(F)$ is the mean of $F$. This choice corresponds to optimizing average performance of the system. In typical engineering applications, however, this is not sufficient and more conservative risk measures need to be chosen.
  \item $R(F)=\sup(F)$. This is the most conservative case, in which one is concerned with the worst case performance of the system. The expression $\sup(F)$ stands for the least of all values that are greater than the random response $F$ with probability 1. If the support of the probability density function (PDF) of $F$ is not compact (i.e. $F$ can take arbitrary large values with non-zero probability) than $\sup(F)$ will be infinite.
  \item $R(F)=\mu(F)+k\sigma(F)$, where $\sigma(F)$ is the standard deviation of $F$ and $k>0$ is a constant. This risk measure is sometimes referred to as the safety margin. Optimization using this risk measure is referred to as robust design optimization \cite{KochYangGu2004,Yao2011,ZhangZhuChenArendt2013} and reflects the paradigms of a ‘$3\sigma$-design’, a ‘$6\sigma$-design’, etc.
  \item $R(F)=q_F(\alpha)$, where $q_F(\alpha)$ is the value of the quantile function, or simply the quantile, corresponding to a given probability $\alpha\in (0,1)$. This choice corresponds to the paradigm of reliability-based design optimization  \cite{AouesChateauneuf2010,Yao2011,YounChoi2004}. In this approach, one wants to keep the probability of the system failing (i.e. violating the constraint or underperforming, depending on the context) below a given threshold. The value $1-\alpha$ is the desired probability of failure. Although rather intuitive, this choice has known computational issues which are discussed by Rockafellar and Royset \cite{RockafellarRoyset2010}.
  \item $R(F)=\overline{q}_F(\alpha)$, where $\overline{q}_F(\alpha)$ is the \textit{superquantile} introduced by Rockafellar and Uryasev \cite{RockafellarUryasev2000} and $\alpha \in (0,1)$ is a parameter. The $\alpha$-superquantile can be interpreted as the so-called \textit{buffered probability of failure}. The buffered probability of failure is always slightly more conservative than the usual probability of failure and, therefore, optimizing with respect to the buffered probability, one automatically gets constraints on the conventional probability of failure. It was found by Basova, Rockafellar, and Royset \cite{BasovaRockafellarRoyset} based on a number of engineering examples that the buffered probability of failure typically overestimates the conventional probability of failure by a factor of 3. 	
\end{itemize}

Superquantiles exhibit significantly better numerical properties than usual quantiles \cite{RockafellarRoyset2010}. The $\alpha$-superquantile can also be interpreted either as an average of quantiles  for $\alpha < \beta <1$, or as the conditional expectation of $F$ in its $(1−\alpha)$-tail \cite{RockafellarRoyset2015}:
\[
\overline{q}_F(\alpha) = \frac{1}{1-\alpha} \int_\alpha^1q_F(\beta)d\beta ;
\]
\[
\overline{q}_F(\alpha) = E\left[F|F\geq q_F(\alpha)\right],
\]
where $E\left[F|F\geq q_F(\alpha)\right]$ is the conditional expectation of $F$ (conditional mean). The superquantile corresponding to $\alpha = 0$ is just the mean $\mu(F)=E[F]$.

@@

To compute the safety margin risk measure, one needs to compute two integrals:
\begin{displaymath}
  \begin{array}{c}
    \mu (F)=E[F]=\int F(\pmb x + \pmb u, \pmb y)p df(\pmb u, \pmb y)d\pmb u d\pmb y \\
    \sigma^2(F)=E[(F-E[F])^2]=\\\int(F(\pmb x + \pmb u, \pmb y)-E[F])^2 p df(\pmb u, \pmb y)d\pmb u d\pmb y
  \end{array}
\end{displaymath}

@@

Computation of the superquantile is not much more involved than calculating expectations, although it is not straightforward to see from its definition. A simple formula for the superquantile exists \cite{RockafellarUryasev2000,RockafellarRoyset2015} that combines computation of an expected value and solution of an auxiliary convex one-dimensional optimization problem:
    \begin{equation} \label{eq:auxiliary_problem}
			\overline{q}_F(\alpha) = \min_c\{c+E[(F-c)_+]\},
    \end{equation}
where where ($F-c)_+$ denotes the positive part of the function $(F(\pmb x+ \pmb u,\pmb y) - c)_+$ (i.e. $F(\pmb x+ \pmb u,\pmb y) - c)$, if this value is positive, and zero otherwise), $E[\cdot]$ is, as before, the expected value, and $c$ is a scalar. It has been shown by Rockafellar and Uryasev \cite{RockafellarUryasev2000} that the function to be minimized in (\ref{eq:auxiliary_problem}) is convex and continuously differentiable in $c$ if the underlying distribution is continuous. Therefore, the minimum in (\ref{eq:auxiliary_problem}) can be easily found using an appropriate one-dimensional convex optimization technique, e.g. the golden search, which was used in the examples in the next section. The integral (expectation) in (\ref{eq:auxiliary_problem}) can be approximated using the quasi-Monte-Carlo method. To solve the auxiliary optimization problem (\ref{eq:auxiliary_problem}), one would need to compute the expectation several times with different values of $c$. It should be noted, however, that this procedure does not require any additional evaluations of the response $F$ as the same samples can be used every time. Therefore, the solution of the auxiliary optimization problem (\ref{eq:auxiliary_problem}) does not present any significant additional computational challenges.

@@

The $\mu(F ) + k\sigma(F)$ risk measure uses quantities that are estimated in the middle of the distribution --- the mean and the standard deviation. On the one hand, this has the advantage that samples drawn directly from the distribution of the random variables $\pmb u$ and $\pmb y$ are well suited to approximately compute this risk measure. On the other hand, probabilistic interpretation of the obtained results in this case is only possible under the normality assumption for the distribution of $F$; if the actual distribution of $F$ has heavier tails than the normal one, the actual probability of failure will be higher than the one  the system was designed for.

>>>>

Optimization under uncertainty deals with responses $F(\boldsymbol x,\boldsymbol y)$ that depend on deterministic design variables $\boldsymbol x$ and random ``environmental'' variables $\boldsymbol y$. Uncertainty in the design variables can also be modelled by introducing additional random variables, e.g. as additive or multiplicative noise. In this case, the responses $F(\boldsymbol x,\boldsymbol y)$ receive as input the sum $\boldsymbol x+\boldsymbol u$ (if the noise is additive), where $\boldsymbol u$ is a random variable with a known probability distribution, yielding responses depending on $\boldsymbol x,\; \boldsymbol u$ and $\boldsymbol y$. Randomness in $\boldsymbol u$ and $\boldsymbol y$ induces randomness in the responses $F(\boldsymbol x+\boldsymbol u,\boldsymbol y)$. To convert them into deterministic functions, that can be optimized, a mapping $R$, called the \textit{risk measure} \cite{RockafellarUryasev2000} or \textit{robustness measure} \cite{SchillingsSchulz2015}, is applied to the responses. The result is then a deterministic function of the design variables: $\widetilde{F}(\boldsymbol x)=R(F(\boldsymbol x+\boldsymbol u, \boldsymbol y))$. The choice of a particular risk measure $R$ reflects the designer's attitude towards the risk of sub-optimal performance or constraint violation. For example, $R$ can be a combination of the mean and standard deviation of $F(\boldsymbol x+ \boldsymbol u,\boldsymbol y)$ with respect to the joint probability distribution of $\boldsymbol u$ and $\boldsymbol y$ or a quantile of the distribution of $F(\boldsymbol x+ \boldsymbol u,\boldsymbol y)$, i.e. such a value that the random variable of $F(\boldsymbol x+\boldsymbol u,\boldsymbol y)$ exceeds it with a given, typically small, probability.

Computations of the risk measures typically involve evaluation of high-di\-mensional integrals, which becomes a challenging task if the number of design variables and/or environmental variables is large. The problem becomes even more difficult if the original responses are computationally expensive, which is the case, for example, in computational fluid dynamics (CFD), where one function evaluation may take hours of even days. Therefore, direct computation of the risk measures using original responses becomes infeasible and therefore approximations of responses, also referred to as metamodels, need to be used.

@@

It is useful to start with a brief description of the deterministic version of MAM. A typical formulation of a constrained optimization problem that MAM works with is as follows:
\begin{equation}
  \label{eq:problem}
  \begin{array}{c}
  \min\limits_{a_i \le x_i \le b_i}F_0(\boldsymbol x) \\
  s.t.\; F_j(\boldsymbol x) \le 1,\; j=1,\dots ,M,
  \end{array}
\end{equation}
where $\boldsymbol x$ is the vector of design variables, $\boldsymbol a$ and $\boldsymbol b$ are the lower and upper bounds for the design variables, respectively, $F_0(\boldsymbol x)$ is the objective function, and $F_j(\boldsymbol x)$ are the constraints. The numbers of design variables and constraints are $n$ and $M$, respectively. MAM attempts to solve this problem by using approximations of the objective function and constraints in a series of trust regions. The trust region strategy seeks to zoom in on the region where the constrained minimum is achieved. It aims at finding a trust region that is sufficiently small for the approximations to be of sufficiently good quality to improve the design, and that contains the point of the constrained minimum as its interior point. The main loop of the MAM is organized as follows.

Algorithm 1 (deterministic MAM).
\begin{enumerate}
\item Initialization: choose a starting point $\boldsymbol x^0$ and initial trust region $[\boldsymbol a^0, \boldsymbol b^0]$ such that $\boldsymbol x^0 \in [\boldsymbol a^0, \boldsymbol b^0]$.
\item At the $k$-th iteration the current approximation to the constrained minimum is $\boldsymbol x^k$, the current trust region is $[\boldsymbol a^k, \boldsymbol b^k] \subset [\boldsymbol a^0, \boldsymbol b^0]$.
  \begin{enumerate}[label=(\alph*)]
    \item Design of Experiments (DoE): a set of points $\boldsymbol x_k^i \in [\boldsymbol a^k, \boldsymbol b^k]$ is chosen to be used for approximation building. Responses are evaluated at the DoE points and approximations are built using the obtained values. Currently, the pool of approximation methods available in MAM consists of a metamodel assemblies \cite{PolynkinToropov2012} and the moving least-squares metamodels \cite{LancasterSalkauskas1981,Liszka1984,ChoiYounYang2001,ToropovSchrammSahaiJones2005}. Other metamodel types could be used as well.

    Denote the approximate objective function and constraints by $\widetilde{F}_0(\boldsymbol x)$ and $\widetilde{F}_j(\boldsymbol x)$, respectively.
    \item The original optimization problem (\ref{eq:problem}) is replaced by the following problem:
    \begin{equation}
      \label{eq:problem_approx}
      \begin{array}{c}
      \min\limits_{a_i^k \le x_i\le b_i^k}\widetilde{F}_0(\boldsymbol x) \\
      s.t.\; \widetilde{F}_j(\boldsymbol x) \le 1,\; j=1,\dots ,M.
      \end{array}
    \end{equation}
    The approximate problem (\ref{eq:problem_approx}) is solved using Sequential Quadratic Programming (SQP) and the solution of this problem determines the center of the next trust region.
    \item The size of the next trust region is determined depending on the quality of approximations at the previous iteration, on the history of the points $\boldsymbol x^k$, and on the size of the current trust region \cite{KeulenToropovMarkine1996}.
    \item The termination criterion is checked (it is a part of the trust region strategy and depends on the position of the point $\boldsymbol x^{k+1}$ in the current trust region, the size of the current trust region and the quality of approximations). If the termination criterion is satisfied, the algorithm proceeds to step 3. Otherwise, it returns to step 2.
  \end{enumerate}
  \item Optimization terminates. The obtained approximation to the solution of the problem (\ref{eq:problem}) is $\boldsymbol x^{k+1}$.
\end{enumerate}

@@

The presence of uncertainties in the responses requires certain reformulations in the problem statement (\ref{eq:problem}). Informally, the optimization problem with uncertainty can be written as follows:
\begin{equation}
  \label{eq:problem_unc}
  \begin{array}{c}
  \min\limits_{a_i \le x_i \le b_i}F_0(\boldsymbol x + \boldsymbol u, \boldsymbol y) \\
  s.t.\; F_j(\boldsymbol x + \boldsymbol u, \boldsymbol y) \le 1,\; j=1,\dots ,M,
  \end{array}
\end{equation}
where the random variable $\boldsymbol u$ represents (additive) noise in the design variables and $\boldsymbol y$ is the environmental variable, representing input to the responses that cannot be influenced by the designer. This problem statement is not precise since the random responses $F_0 (\boldsymbol x+\boldsymbol u,\boldsymbol y),\; F_j (\boldsymbol x+\boldsymbol u,\boldsymbol y)$ cannot be directly optimized. Therefore, a risk measure $R$ needs to be applied to the objective and the constraints:
\begin{equation}
  \label{eq:problem_unc_r}
  \begin{array}{c}
  \min\limits_{a_i \le x_i \le b_i}R_{u,y}(F_0)(\boldsymbol x) \\
  s.t.\; R_{u,y}(F_j)(\boldsymbol x) \le 1,\; j=1,\dots ,M,
  \end{array}
\end{equation}
where the subscript in $R_{u,y}$ indicates that the variables $\boldsymbol u$ and $\boldsymbol y$ ‘collapse’ when the risk measure is applied and the result only depends on $\boldsymbol x$. The choices of risk measure will be discussed in Section \ref{sec:risk}. Here the changes in the Algorithm 1 that are necessary to solve the problem (\ref{eq:problem_unc_r}) are discussed.

First, it needs to be decided on whether to build metamodels for the risk measure $R_{u,y}(F_j)(\boldsymbol x)$ or for the original responses $F_j (\boldsymbol x+ \boldsymbol u,\boldsymbol y)$. The first option may seem attractive due to the simplicity of its implementation in Algorithm 1 but the deciding argument has to be that of the computational cost associated with the evaluation of either function. On the one hand, one evaluation of the function $R_{u,y}(F_j)(\boldsymbol x)$ involves computing one or several integrals of the original response $F_j(\boldsymbol x+ \boldsymbol u,\boldsymbol y)$ over the distribution of $\boldsymbol u$ and $\boldsymbol y$, which requires many evaluations of the original response. On the other hand, the dimensionality of the argument of $R_{u,y}(F_j)(\boldsymbol x)$ is less than that of the argument of $F_j(\boldsymbol x+ \boldsymbol u,\boldsymbol y)$, therefore, in principle, fewer function evaluations are needed to approximate the former than the latter. In practice, this may be a matter of a trade-off between the two abovementioned effects that depends on the proportion between the numbers of design variables $n$ and the environmental variables $n_e$ and on the complexity of the integration method and metamodeling method used. If the number if design variables is significantly larger than the number of environmental variables, which is often the case and which is assumed in this paper, building metamodels for the original responses $F_j(\boldsymbol x+ \boldsymbol u,\boldsymbol y)$ is preferred.

@@

Algorithm 2 (MAM under uncertainty).
\begin{enumerate}
%  \item Initialization: choose a starting point $\boldsymbol x_0 \in {\Bbb R}^n$. 
  \item Initialization: choose a starting point $\boldsymbol x_0 \in {\boldsymbol R}^n$. 
	Choose an initial trust region $[\boldsymbol a^0,\boldsymbol b^0]$ in the combined space of design variables and environmental variables. 
	Ensure that the initial guess $\boldsymbol x_0$ belongs to the projection of the initial trust region onto the subspace of design variables. The projection of the initial trust region onto the subspace of environmental variables must cover the region where the realizations of the random variable y are likely to be. The coordinates of the trust region corresponding to the environmental variables will not be changed in the course of optimization. Typically, the trust region along the coordinates corresponding to the $i$-th environmental variable is centered at the mean of the $i$-th environmental variable and has the width of six of its standard deviations.
  \item At the $k$-th iteration the current approximation to the constrained minimum is $\boldsymbol x^k$, the current trust region is $[\boldsymbol a^k,\boldsymbol b^k]$.
  \begin{enumerate}[label=(\alph*)]
    \item Design of Experiments (DoE): a set of points $(x_i^k,y_i^k)\in [\boldsymbol a^k,\boldsymbol b^k]$ is chosen that will be used to build approximations. Responses are evaluated at the DoE points and approximations are built using the obtained values.
    Denote the approximate objective function and constraints by $\widetilde{F}_0(\boldsymbol x, \boldsymbol y)$ and $\widetilde{F}_j(\boldsymbol x, \boldsymbol y)$, respectively.
    \item The original optimization problem is replaced by the following problem:
    \begin{equation}
      \label{eq:problem_u_tilde}
      \begin{array}{c}
      \min\limits_{a_i^k \le x_i \le b_i^k}R_{u,y}(\widetilde{F}_0)(\boldsymbol x) \\
      s.t.\; R_{u,y}(\widetilde{F}_j)(\boldsymbol x) \le 1,\; j=1,\dots ,M,
      \end{array}
    \end{equation}
    The risk measures are calculated using the metamodels obtained in the previous step. Integrals that arise during this process are calculated with respect to the joint distribution of $\boldsymbol u$ and $\boldsymbol y$. This distribution is assumed to be fixed.
    The approximate problem (\ref{eq:problem_u_tilde}) is solved using Sequential Quadratic Programming (SQP) and the center of the next trust region $\boldsymbol x^{k+1}$ is determined as the solution of this problem. The optimization runs in a subspace of the space where metamodels are built: metamodels are defined in the combined space of design variables and environmental variables, whilst optimization runs in the subspace of the design variables.
    \item The trust region is updated. The size of the trust region along the dimensions corresponding to the environmental variables is unchanged. The size of the next trust region along the dimensions corresponding to the design variables is determined depending on the quality of approximations at the previous iteration, on the history of the points $\boldsymbol x^k$, and on the size of the current trust region according to the trust region strategy explained in \cite{KeulenToropovMarkine1996}.
    \item The termination criterion is checked. If the termination criterion is satisfied, the algorithm proceeds to step 3. Otherwise, it returns to step 2
  \end{enumerate}
  \item Optimization terminates. The obtained approximation to the optimum is $\boldsymbol x^{k+1}$.
\end{enumerate}

@@

As it has been already said, a risk measure is a mapping that transforms a random response $F(\boldsymbol x+ \boldsymbol u,\boldsymbol y)$  into a deterministic function that can be optimized. Next we provide some examples of risk measures \cite{RockafellarUryasev2000,SchillingsSchulz2015}.

\begin{itemize}
  \item $R(F)=\mu(F)$ where $\mu(F)$ is the mean of $F$. This choice corresponds to optimizing average performance of the system. In typical engineering applications, however, this is not sufficient and more conservative risk measures need to be chosen.
  \item $R(F)=\sup(F)$. This is the most conservative case, in which one is concerned with the worst case performance of the system. The expression $\sup(F)$ stands for the least of all values that are greater than the random response $F$ with probability 1. If the support of the probability density function (PDF) of $F$ is not compact (i.e. $F$ can take arbitrary large values with non-zero probability) than $\sup(F)$ will be infinite.
  \item $R(F)=\mu(F)+k\sigma(F)$, where $\sigma(F)$ is the standard deviation of $F$ and $k>0$ is a constant. This risk measure is sometimes referred to as the safety margin. Optimization using this risk measure is referred to as robust design optimization \cite{KochYangGu2004,Yao2011,ZhangZhuChenArendt2013} and reflects the paradigms of a ‘$3\sigma$-design’, a ‘$6\sigma$-design’, etc.
  \item $R(F)=q_F(\alpha)$, where $q_F(\alpha)$ is the value of the quantile function, or simply the quantile, corresponding to a given probability $\alpha\in (0,1)$. This choice corresponds to the paradigm of \textit{reliability-based design optimization} \cite{AouesChateauneuf2010,Yao2011,YounChoi2004}. In this approach, one wants to keep the probability of the system failing (i.e. violating the constraint or underperforming, depending on the context) below a given threshold. The value $1-\alpha$ is the desired probability of failure. Although rather intuitive, this choice has known computational issues which are discussed by Rockafellar and Royset \cite{RockafellarRoyset2010}.
  \item $R(F)=\overline{q}_F(\alpha)$, where $\overline{q}_F(\alpha)$ is the \textit{superquantile} introduced by Rockafellar and Uryasev \cite{RockafellarUryasev2000} and $\alpha \in (0,1)$ is a parameter. The $\alpha$-superquantile can be interpreted as the so-called \textit{buffered probability of failure}. The buffered probability of failure is always slightly more conservative than the usual probability of failure and, therefore, optimizing with respect to the buffered probability, one automatically gets constraints on the conventional probability of failure. It was found by Basova, Rockafellar, and Royset \cite{BasovaRockafellarRoyset} based on a number of engineering examples that the buffered probability of failure typically overestimates the conventional probability of failure by a factor of 3. 	
\end{itemize}

Superquantiles exhibit significantly better numerical properties than usual quantiles \cite{RockafellarRoyset2010}. The $\alpha$-superquantile can also be interpreted either as an average of quantiles  for $\alpha < \beta <1$, or as the conditional expectation of $F$ in its $(1-\alpha)$-tail \cite{RockafellarRoyset2015}:
\[
\overline{q}_F(\alpha) = \frac{1}{1-\alpha} \int_\alpha^1q_F(\beta)d\beta ;
\]
\[
\overline{q}_F(\alpha) = E\left[F|F\geq q_F(\alpha)\right],
\]
where $E\left[F|F\geq q_F(\alpha)\right]$ is the conditional expectation of $F$ (conditional mean). The superquantile corresponding to $\alpha = 0$ is just the mean $\mu(F)=E[F]$.

@@

To compute the safety margin risk measure, one needs to compute two integrals:
\begin{gather*}
    \mu (F)=E[F]=\int F(\boldsymbol x + \boldsymbol u, \boldsymbol y)p df(\boldsymbol u, \boldsymbol y)d\boldsymbol u d\boldsymbol y \\
    \sigma^2(F)=E[(F-E[F])^2]=\int(F(\boldsymbol x + \boldsymbol u, \boldsymbol y)-E[F])^2 p df(\boldsymbol u, \boldsymbol y)d\boldsymbol u d\boldsymbol y
\end{gather*}

@@

Computation of the superquantile is not much more involved than calculating expectations, although it is not straightforward to see from its definition. A simple formula for the superquantile exists \cite{RockafellarUryasev2000,RockafellarRoyset2015} that combines computation of an expected value and solution of an auxiliary convex one-dimensional optimization problem:
    \begin{equation} \label{eq:auxiliary_problem}
			\overline{q}_F(\alpha) = \min_c\{c+E\left[(F-c)_+\right]\},
    \end{equation}
where where ($F-c)_+$ denotes the positive part of the function $F(\boldsymbol x+ \boldsymbol u,\boldsymbol y) - c$ (i.e. $F(\boldsymbol x+ \boldsymbol u,\boldsymbol y) - c$, if this value is positive, and zero otherwise), $E[\cdot]$ is, as before, the expected value, and $c$ is a scalar. It has been shown by Rockafellar and Uryasev \cite{RockafellarUryasev2000} that the function to be minimized in (\ref{eq:auxiliary_problem}) is convex and continuously differentiable in $c$ if the underlying distribution is continuous. Therefore, the minimum in (\ref{eq:auxiliary_problem}) can be easily found using an appropriate one-dimensional convex optimization technique, e.g. the golden search, which was used in the examples in the next section. The integral (expectation) in (\ref{eq:auxiliary_problem}) can be approximated using the quasi-Monte-Carlo method. To solve the auxiliary optimization problem (\ref{eq:auxiliary_problem}), one would need to compute the expectation several times with different values of $c$. It should be noted, however, that this procedure does not require any additional evaluations of the response $F$ as the same samples can be used every time. Therefore, the solution of the auxiliary optimization problem (\ref{eq:auxiliary_problem}) does not present any significant additional computational challenges.

@@

The $\mu(F ) + k\sigma(F)$ risk measure uses quantities that are estimated in the middle of the distribution --- the mean and the standard deviation. On the one hand, this has the advantage that samples drawn directly from the distribution of the random variables $\boldsymbol u$ and $\boldsymbol y$ are well suited to approximately compute this risk measure. On the other hand, probabilistic interpretation of the obtained results in this case is only possible under the normality assumption for the distribution of $F$; if the actual distribution of $F$ has heavier tails than the normal one, the actual probability of failure will be higher than the one  the system was designed for.
